Report

### 2023-07-06 script/report.Rmd
update report

---
title: "Report"
author: " "
date: "2022-08-16"
output:
    html_document:
        highlight: tango
        number_sections: yes
        theme: default
        toc: yes
        toc_depth: 3
        toc_float:
            collapsed: yes
            smooth_scroll: yes
params:
  DP.min: DP.min
  AR.min: AR.min
  qual.min: qual.min
  result_dir: result_dir
  sample_sheet: sample_sheet
  rmd: "report.Rmd"
  AR: AR
---

```{r}
# title: "`r params$title`"
workspace <-params$result_dir
sample_sheet.file <- params$sample_sheet
# DP.min <- params$DP.min
# AR.min <- params$AR.min
# qual.min <- params$qual.min

#Genome.file <- "/save/project/ijpb/bank/GENOME/Ppatens-patens-v3.3-WG/Ppatens-patens-v3.3-WG.fa"
projectName <- "PE-WGS"

@@

DP.min <- 4
AR.min <- 0.8
qual.min <- 30
nbr.alt.min <- 3
```

>>>>

---
title: "Report"
author: " "
date: "2022-08-16"
output:
    html_document:
        highlight: tango
        number_sections: yes
        theme: default
        toc: yes
        toc_depth: 3
        toc_float:
            collapsed: yes
            smooth_scroll: yes
params:
  DP.min: DP.min
  AR.min: AR.min
  qual.min: qual.min
  result_dir: result_dir
  sample_sheet: sample_sheet
  projectName : projectName
  rmd: "report.Rmd"
  AR: AR
---

```{r}
# title: "`r params$title`"
workspace <-params$result_dir
sample_sheet.file <- params$sample_sheet
DP.min <- params$DP.min
AR.min <- params$AR.min
qual.min <- params$qual.min
projectName <- params$projectName
#Genome.file <- "/save/project/ijpb/bank/GENOME/Ppatens-patens-v3.3-WG/Ppatens-patens-v3.3-WG.fa"
#projectName <- "PE-WGS"

@@

# DP.min <- 4
# AR.min <- 0.8
# qual.min <- 30
nbr.alt.min <- 3
```
